Exercise 1: Naming Functions

A good function name is a verb or short phrase that tells you what the function does without having to read its body. Badly named functions (f1, do_stuff, helper2) force every reader — including future-you — to re-derive intent from the code each time.

1.Read the source code for each of the following two functions, puzzle out what they do, and then brainstorm better names.

```{r}
f1 <- function(string, prefix) {
  str_sub(string, 1, str_length(prefix)) == prefix
}
# This function checks whether a given string starts with a specified prefix. It extracts the beginning of the string with the same length as the prefix and compares it to the prefix.Better name:starts_with_prefix
f3 <- function(x, y) {
  rep(y, length.out = length(x)) #把y重复直到等于x元素个数
}
# This function repeats the value y so that the output has the same length as x. It ensures that y matches the length of x. Better name: repeat_to_length
```

2.Make a case for why norm_r(), norm_d() etc. would be better than rnorm(), dnorm()1. Make a case for the opposite. How could you make the names even clearer?

Case for norm_r(), norm_d() (distribution first)
Using names like norm_r() and norm_d() makes the distribution the primary concept and the operation secondary.
Improved grouping and discover ability
More intuitive for beginners
Consistent with object → action logic

Case for rnorm(), dnorm() (operation first)
R’s existing naming (rnorm, dnorm, etc.) prioritizes the type of operation.
Consistency across all distributions
The prefixes (r, d, p, q) are standardized and widely understood.
r = random
d = density
p = probability
q = quantile
Efficient for experienced users
If you know you want random numbers, you type r... and choose the distribution.
This supports a workflow of “what do I want to do?” → “to which distribution?”
Compact and fast to type
Short names reduce typing overhead and visual clutter.

even clearer: 
Fully descriptive (maximum clarity); 
Tidy-style compromise
r_norm()
d_norm()
p_norm()
q_norm()

Exercise 2: Using Functions to Package Code
Last week you wrote a bit of code to filter and plot the palmerpenguins data. Copy-pasting that code every time you want the same plot for a different species is a recipe for bugs — the moment you change one copy and forget the others, your plots start disagreeing. Turning the code into a function fixes this: there is one place that defines the behaviour, and you invoke it with different arguments.

1.Take a look at the following code. Wrap this code in a function with a fitting name and appropriate arguments.

2.Add a docstring to your function that explains what the function does, its arguments, and its return value.

```{r}
library(palmerpenguins)
library(tidyverse)

penguins %>%
  filter(species == "Adelie") %>%
  ggplot(aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point() +
  labs(title = "Bill Length vs. Bill Depth for Adelie Penguins",
       x = "Bill Length (mm)",
       y = "Bill Depth (mm)")
```
```{r}
library(palmerpenguins)
library(tidyverse)
plot_bill_scatter <- function(penguins, species_name) {
  penguins %>% 
    filter(species == species_name) %>%
  ggplot(aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point() +
  labs(title = paste("Bill Length vs. Bill Depth for", species_name, "Penguins"),
       x = "Bill Length (mm)",
       y = "Bill Depth (mm)"
       )
}
#test
unique(penguins$species)
plot_bill_scatter(penguins, "Gentoo")
```

```{r}
#' Plot a scatter plot for penguin data
#'
#' This function filters the dataset for a given species and creates
#' a scatter plot of two selected variables.
#'
#' @param data A data frame containing penguin data.
#' @param species_name A character string specifying the species (e.g., "Adelie").
#' @param x_var A variable for the x-axis.
#' @param y_var A variable for the y-axis.
#' @param title An optional title for the plot. If NULL, a default title is generated.
#'
#' @return A ggplot object representing the scatter plot.
#'
#' @examples
#' plot_penguin_scatter(penguins, "Adelie", bill_length_mm, bill_depth_mm)
#' plot_penguin_scatter(penguins, "Gentoo", flipper_length_mm, body_mass_g)

plot_penguin_scatter <- function(data, species_name, x_var, y_var, title = NULL) {
  # check input
  if (!species_name %in% unique(data$species)) {
    stop("Invalid species name.")
  }
  # If no title is provided, it will be generated automatically.
  if (is.null(title)) {
    title <- paste("Scatter plot of", deparse(substitute(x_var)), 
                   "vs", deparse(substitute(y_var)), 
                   "for", species_name)
  }
  
  data %>%
    dplyr::filter(species == species_name) %>%
    ggplot2::ggplot(ggplot2::aes(x = {{ x_var }}, y = {{ y_var }})) +
    ggplot2::geom_point() +
    ggplot2::labs(
      title = title,
      x = deparse(substitute(x_var)),
      y = deparse(substitute(y_var))
    )
}
#test
plot_penguin_scatter(penguins, "Adelie", body_mass_g, flipper_length_mm, title = NULL)
```

3.Test your function by calling it with different arguments and checking the output. Make sure to test edge cases:
What happens if you pass in a species name that doesn’t exist (e.g. "Penguin")?
What happens if you pass a column name that isn’t in the data (e.g. x_var = "fluffiness")?
What happens if you pass a non-numeric column (e.g. x_var = "island")?
Write down what you expect to happen for each case before running it — are the actual errors informative? We’ll fix the bad ones in Exercise 3.

```{r}
#test

plot_penguin_scatter(penguins, "Penguin", body_mass_g, flipper_length_mm)
#error "Invalid species name"

plot_penguin_scatter(penguins, "Adelie", island, flipper_length_mm, title = NULL)
#silent failure

plot_penguin_scatter(penguins, "Penguin", fluffiness, flipper_length_mm)
#error "Invalid species name."
```

4.Split your function into smaller helper functions. One function should only perform one task.

Then rewrite plot_penguin_bills() to just call these two helpers in sequence. The top-level function becomes shorter and easier to read, and each helper is independently testable.

```{r}
filter_species <- function(data, species_name) {
  if (!species_name %in% unique(data$species)) {
    stop("Invalid species name.")
  }
  filter(data, species == species_name)
}

make_scatter_plot <- function(data, x_var, y_var, title = NULL) {
  if (is.null(title)) {
    title <- paste("Scatter plot of",
                   deparse(substitute(x_var)),
                   "vs",
                   deparse(substitute(y_var)))
  }

  ggplot(data, ggplot2::aes(x = {{ x_var }}, y = {{ y_var }})) +
    geom_point() +
    labs(
      title = title,
      x = deparse(substitute(x_var)),
      y = deparse(substitute(y_var))
    )
}

plot_penguin_bills <- function(data, species_name, x_var, y_var, title = NULL) {
  data_filtered <- filter_species(data, species_name)
  make_scatter_plot(data_filtered, x_var, y_var, title)
}
```

Exercise 3: Error Handling
1.Add input validation to plot_penguin_bills() from Exercise 2 so that it fails with a useful message when:
species is not one of the three valid species ("Adelie", "Chinstrap", "Gentoo").
x_var or y_var is not a column of the penguins data frame.
x_var or y_var refers to a non-numeric column.

2.Compare the error messages you get now vs. before. Which version would be easier to debug at 11pm the night before an assignment deadline?

Answer: The updated version provides much more informative and user-friendly error messages.
Instead of generic errors such as "object not found" or silent failures, the function now explicitly checks inputs and explains what went wrong and how to fix it.
This makes debugging significantly easier, because the user can quickly identify the issue without having to trace through the code.

Input validation
```{r}
plot_penguin_bills <- function(data, species_name, x_var, y_var, title = NULL) {
  
  # ---- 1. 检查 species ----
  valid_species <- c("Adelie", "Chinstrap", "Gentoo")
  if (!species_name %in% valid_species) {
    stop("Invalid species. Must be one of: ", paste(valid_species, collapse = ", "))
  }
  
  # ---- 2. 检查列是否存在 ----
  x_name <- deparse(substitute(x_var))
  y_name <- deparse(substitute(y_var))
  
  if (!x_name %in% names(data)) {
    stop("Column '", x_name, "' not found in data.")
  }
  
  if (!y_name %in% names(data)) {
    stop("Column '", y_name, "' not found in data.")
  }
  
  # ---- 3. 检查是否为数值型 ----
  if (!is.numeric(data[[x_name]])) {
    stop("Column '", x_name, "' must be numeric.")
  }
  
  if (!is.numeric(data[[y_name]])) {
    stop("Column '", y_name, "' must be numeric.")
  }
  
  # ---- 4. 生成默认标题 ----
  if (is.null(title)) {
    title <- paste("Scatter plot of", x_name, "vs", y_name, "for", species_name)
  }
  
  # ---- 5. 正常执行 ----
  data %>%
    dplyr::filter(species == species_name) %>%
    ggplot2::ggplot(ggplot2::aes(x = {{ x_var }}, y = {{ y_var }})) +
    ggplot2::geom_point() +
    ggplot2::labs(title = title, x = x_name, y = y_name)
}
```
cli Version
```{r}
library(cli)
plot_penguin_bills <- function(data, species_name, x_var, y_var, title = NULL) {
  
  # ---- 1. 检查 species ----
  valid_species <- c("Adelie", "Chinstrap", "Gentoo")
  
  if (!species_name %in% valid_species) {
    cli::cli_abort(c(
      "Invalid {.arg species_name}.",
      "x" = "You provided: {.val {species_name}}",
      "i" = "Valid options are: {.val {valid_species}}"
    ))
  }
  
  # ---- 2. 获取变量名 ----
  x_name <- deparse(substitute(x_var)) 
  y_name <- deparse(substitute(y_var))
# substitute() = 拿到“代码本身”，deparse() = 转成字符串
  
  # ---- 3. 检查列是否存在 ----
  if (!x_name %in% names(data)) {
    cli::cli_abort(c(
      "Column {.val {x_name}} not found in {.arg data}.",
      "i" = "Available columns: {.val {names(data)}}"
    ))
  }
  
  if (!y_name %in% names(data)) {
    cli::cli_abort(c(
      "Column {.val {y_name}} not found in {.arg data}.",
      "i" = "Available columns: {.val {names(data)}}"
    ))
  }
  
  # ---- 4. 检查是否 numeric ----
  if (!is.numeric(data[[x_name]])) {
    cli::cli_abort(c(
      "Column {.val {x_name}} must be numeric.",
      "x" = "Current type: {.val {class(data[[x_name]])}}"
    ))
  }
  
  if (!is.numeric(data[[y_name]])) {
    cli::cli_abort(c(
      "Column {.val {y_name}} must be numeric.",
      "x" = "Current type: {.val {class(data[[y_name]])}}"
    ))
  }
  
  # ---- 5. 默认标题 ----
  if (is.null(title)) {
    title <- paste("Scatter plot of", x_name, "vs", y_name, "for", species_name)
  }
  
  # ---- 6. 绘图 ----
  data %>%
    dplyr::filter(species == species_name) %>%
    ggplot2::ggplot(ggplot2::aes(x = {{ x_var }}, y = {{ y_var }})) +
    ggplot2::geom_point() +
    ggplot2::labs(title = title, x = x_name, y = y_name)
}
```
test
```{r}
plot_penguin_bills(penguins, "Penguin", body_mass_g, flipper_length_mm, title = NULL)

plot_penguin_bills(penguins, "Adelie", island, species, title = NULL)

plot_penguin_bills(penguins, "Adelie", body_mass_g, flipper_length_mm, title = NULL)
```

